Reproducibility and plant pathology: where do we stand and a way forward

### 2021-06-16 analysis/paper/paper.Rmd
Follow APS heading style
Remove unnecessary YAML options
these are defined in the template Word file

---
title: "Reproducibility and plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique dos Santos Alves:
      institute: UFV
  - Zachary Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97331, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/template.docx" # Insert path for the DOCX file
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
classoption: letterpaper
fontsize: 12pt
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
---

@@

## Article Selection

>>>>

---
title: "Reproducibility and plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique dos Santos Alves:
      institute: UFV
  - Zachary Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97331, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/template.docx" # Insert path for the DOCX file
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
---

@@

## Article selection
